\pkg{cv}: An \proglang{R} Package for Cross-Validating Regression Models

### 2024-05-25 scratch/notes_john/JSS-article/JSS-article-3.Rmd
further tweak JSS draft paper

And here's how we can perform the same computation using the \code{cv()} function in the \pkg{cv} package:
```{r rsample-example-using-cv, cache=TRUE}
mod.attrition <- glm(mod_form, data=attrition, family=binomial)
(cv.attrition <- cv(mod.attrition, k="loo", criterion=BayesRule))
```

>>>>

And here's how we can perform the same computation using the \code{cv()} function in the \pkg{cv} package:
```{r rsample-example-using-cv, cache=TRUE}
mod.attrition <- glm(mod_form, data=attrition, family=binomial)
(cv.attrition <- cv(mod.attrition, k="loo", criterion=BayesRule))
all.equal(cv.attrition$`CV crit`, 1 - mean(rs_obj$accuracy), 
          check.attributes=FALSE)
```

### 2024-05-25 scratch/notes_john/JSS-article/JSS-article-3.tex
further tweak JSS draft paper

Residual standard error: 4.374 on 389 degrees of freedom
Multiple R-squared:  0.6876,    Adjusted R-squared:  0.686 
F-statistic:   428 on 2 and 389 DF,  p-value: < 2.2e-16
\end{CodeOutput}
\begin{CodeInput}
R> cv(m.auto, confint=TRUE)
\end{CodeInput}
\begin{CodeOutput}
R RNG seed set to 508110
\end{CodeOutput}
\begin{CodeOutput}
10-Fold Cross Validation
method: Woodbury
criterion: mse
cross-validation criterion = 19.23279
bias-adjusted cross-validation criterion = 19.21953
95% CI for bias-adjusted CV criterion = (15.76747, 22.67159)
full-sample criterion = 18.98477 
\end{CodeOutput}
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> BayesRule
\end{CodeInput}
\begin{CodeOutput}
function(y, yhat) {
  if (!all(y %in% c(0, 1)))
    stop("response values not all 0 or 1")
  if (any(yhat < 0) ||
      any(yhat > 1))
    stop("fitted values outside of interval [0, 1]")
  yhat <- round(yhat)
  result <- mean(y != yhat) # proportion in error
  attr(result, "casewise loss") <- "y != round(yhat)"
  result
}
<bytecode: 0x14aa65750>
<environment: namespace:cv>
\end{CodeOutput}
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> mod.attrition <- glm(mod_form, data=attrition, family=binomial)
R> (cv.attrition <- cv(mod.attrition, k="loo", criterion=BayesRule))
\end{CodeInput}
\begin{CodeOutput}
n-Fold Cross Validation
method: exact
criterion: BayesRule
cross-validation criterion = 0.1612245
bias-adjusted cross-validation criterion = 0.1612245
95% CI for bias-adjusted CV criterion = (0.1424194, 0.1800296)
full-sample criterion = 0.1612245 
\end{CodeOutput}
\end{CodeChunk}

>>>>

Residual standard error: 4.374 on 389 degrees of freedom
Multiple R-squared:  0.6876,    Adjusted R-squared:  0.686 
F-statistic:   428 on 2 and 389 DF,  p-value: < 2.2e-16
\end{CodeOutput}
\begin{CodeInput}
R> cv(m.auto, confint=TRUE)
\end{CodeInput}
\begin{CodeOutput}
R RNG seed set to 866542
\end{CodeOutput}
\begin{CodeOutput}
10-Fold Cross Validation
method: Woodbury
criterion: mse
cross-validation criterion = 19.09701
bias-adjusted cross-validation criterion = 19.09108
95% CI for bias-adjusted CV criterion = (15.65339, 22.52877)
full-sample criterion = 18.98477 
\end{CodeOutput}
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> BayesRule
\end{CodeInput}
\begin{CodeOutput}
function(y, yhat) {
  if (!all(y %in% c(0, 1)))
    stop("response values not all 0 or 1")
  if (any(yhat < 0) ||
      any(yhat > 1))
    stop("fitted values outside of interval [0, 1]")
  yhat <- round(yhat)
  result <- mean(y != yhat) # proportion in error
  attr(result, "casewise loss") <- "y != round(yhat)"
  result
}
<bytecode: 0x13b740948>
<environment: namespace:cv>
\end{CodeOutput}
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> mod.attrition <- glm(mod_form, data=attrition, family=binomial)
R> (cv.attrition <- cv(mod.attrition, k="loo", criterion=BayesRule))
\end{CodeInput}
\begin{CodeOutput}
n-Fold Cross Validation
method: exact
criterion: BayesRule
cross-validation criterion = 0.1612245
bias-adjusted cross-validation criterion = 0.1612245
95% CI for bias-adjusted CV criterion = (0.1424194, 0.1800296)
full-sample criterion = 0.1612245 
\end{CodeOutput}
\begin{CodeInput}
R> all.equal(cv.attrition$`CV crit`, 1 - mean(rs_obj$accuracy), 
+           check.attributes=FALSE)
\end{CodeInput}
\begin{CodeOutput}
[1] TRUE
\end{CodeOutput}
\end{CodeChunk}
